% !TEX encoding = UTF-8 Unicode

\documentclass[a4paper,10pt,twocolumn]{report}
\usepackage[natbibapa,nosectionbib,tocbib,numberedbib]{apacite}

% niet elk chapter op nieuwe pagina
%\let\cleardoublepage\relax \chapter{bar}

\AtBeginDocument{\renewcommand{\bibname}{Literature}}


\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{url}

% corona boxes
\usepackage[dvipsnames]{color}
\usepackage{framed}
\definecolor{shadecolor}{named}{Melon}
%\let\corona\shaded
%\let\endcorona\endshaded
% zo kan het met sterretje:
\newenvironment{corona}{%
	\begin{shaded*}%
	}{%
	\end{shaded*}%
}



\usepackage[colorinlistoftodos]{todonotes}

\usepackage{pifont}

\usepackage{lmodern}
\usepackage{listings}
\lstset{
basicstyle=\scriptsize\ttfamily,
columns=flexible,
breaklines=true,
numbers=left,
%stepsize=1,
numberstyle=\tiny,
backgroundcolor=\color[rgb]{0.85,0.90,1}
}


\let\oldquote\quote
\let\endoldquote\endquote
\renewenvironment{quote}{\footnotesize\oldquote}{\endoldquote}




\title{Big Data and Automated Content Analysis\\ (6 ECTS)\\~\\Course Manual}
\author{dr. Anne Kroon\\~\\Graduate School of Communication\\University of Amsterdam\\~\\a.c.kroon@uva.nl \\@annekroon \\~\\Office: REC-C, 7\textsuperscript{th} floor}


\date{Academic Year 2023/24\\Semester 1, block  1\\ }

\begin{document}
\maketitle

\chapter{About this course}

This course manual contains general information, guidelines, rules and schedules for the Research Master course Big Data \& Automated Content Analysis Part I (6 ECTS). Please make sure you read it carefully, as it  contains information regarding assignments, deadlines and grading.

\section{Course description}

\input{description}

\section{Goals}


Upon completion of this course, the following goals are reached:



\input{testableobjectives}

\section{Help with practical matters}
While making your first steps with programming in Python, you will probably have a lot of questions.
Nevertheless, \url{htttps://google.com} and \url{https://stackoverflow.com} should be your first points of contact. After all, that's how we solve our problems as well\ldots

It is also very much encouraged to try to solve problems together with your classmates. A succesful technique can be \emph{pair programming}, where two colleagues sit behind one screen (for an explanation, see \url{https://en.wikipedia.org/wiki/Pair_programming}).

If you really cannot find a solution on your own, you can pose such questions during the Thursday lab sessions. However, keep the remark in Section~\ref{sec:yourcomputer} in mind!

\chapter{Rules, assignments, and grading}
\input{grading}


\section{Presence and participation}
Attendance is compulsory. Missing more than two meetings – for whatever reason – means the course cannot be completed.

Next to attending the meetings, students are also required to prepare the assigned literature and to continue working on the programming tasks after the lab sessions. To successfully finish the course, attending the lab sessions is not enough, but has to go hand-in-hand with continuous self-study.
\section{Staying informed}
It is your responsibility to check the means of communications used for this course (i.e., your email account, but -- if applicable -- also e-learning platforms or any other tool that the lecturer decides to use) on a regular basis, which in most cases means daily.

\section{Plagiarism \& fraud}
Plagiarism is a serious academic violation. Cases in which students use material such as online sources or any other sources in their written work and present this material as their own original work without citation/referencing, and thus conduct plagiarism, will be reported to the Examencommissie of the Department of Communication without any further negotiation. If the committee comes to the conclusion that a student has indeed committed plagiarism the course cannot be completed.
General UvA regulations about fraud and plagiarism apply, see also \url{https://student.uva.nl/en/content/az/plagiarism-and-fraud/plagiarism-and-fraud.html}.

\subsection{Attributing code}
Plagiarism rules apply to code in the same way as they apply to text. Just like how your writing often builds on other scholars (who you cite), your code often builds on what others have done or are inspired by solutions of others, for instance in communities like Stackoverflow. Analoguous to plagiarism regulations in normal writing, also in your code, it needs to be transparent \emph{what is from you and what is not}. We don't really have something like APA references for code, but you can simply use \texttt{\#comments} for that purpose, such as:
\texttt{\# The following function is copied from https://stackoverflow.com/XXXXX/XXXXX} for (almost) literal copy-pasting, or \texttt{\# The code in this cell is inspired by https://...; I modified Y and Z}. 

Make sure that there is no doubt about what is yours and what is from someone else!

\subsection{Use of AI tools}
It speaks for itself that -- analogous to the rules outlined above -- the use of AI tools such as ChatGPT or Copilot to generate code is not acceptable. Handing in such code will be considered fraud.

\subsection{Working together}
The take-home exams as well as the final project are \emph{individual exams}. Collaboration with fellow students is thus considered academic fraud and will be reported and handled accordingly.


In some instances, some overlap between final projects may be unavoidable, for instance when relying on very similar data sources. If in doubt, always discuss with me in advance to avoid problems after you handed in! It is almost always possible to find a solution, if discussed in advance.

\emph{In contrast to these graded assignments, for all \textbf{ungraded} assignments and exercises, collaboration is explicitly encouraged. Experience with this course over the last decade has shown that those students who met regularly with classmates to go over the week's code examples and exercises together enjoyed the course most, and also performed best.}

\section{Deadlines and handing in}
Per assignment, the lecturer will specify whether it has to be handed in via Canvas or via Filesender. If no specific instructions are given, or if there is any issue with submitting an assignment through Canvas, use Filesender. Please send all assignments and papers as a PDF file (and do not use formats like .docx) to ensure that it can be read and is displayed the same way on any device. Multiple files should be compressed and handed in as one .zip file or .tar.gz file. Do not email assignments directly but send them via \url{https://filesender.surf.nl/} to my mail-address. This way, you can also transfer huge files.

Final papers and take-home exams that are not handed in on time, will be not be graded and receive the grade 1. This rule also applies for any other assignment that might be given. The deadline is only met when the all files are submitted.


\begin{corona}
\section{Your computer and operating system: your responsibility}	
\label{sec:yourcomputer}
Python is a language, not a program, and there are many ways of running Python code. 

It is really hard to help with stuff related to your computer, your operating system, your keyboard etc. Things may work slightly different on Windows compared to MacOS or Linux; it's your responsibility to take care of these things. For instance, a downloaded file may be put under \texttt{/home/damian/Downloads} on Linux, under \texttt{/Users/damian/Downloads} on MacOS, and under \texttt{c:\textbackslash \textbackslash Users \textbackslash \textbackslash Damian\textbackslash \textbackslash Downloads} on Windows -- or maybe something very different. You are expected to have a sufficiently deep understanding of your own computer to deal with these idiosyncrasies yourself.

Therefore you need to make sure that the following things apply. Otherwise, you need to fix it -- we won't have room for that during the course. So, do this \textbf{before the course starts}.

\begin{itemize}
\item You need to have a recent version of a Python interpreter installed, and you need to be able to run Jupyter Notebooks. Chapter 1 of \cite{cssbook} gives instructions (you can skip the part about R, though). You can either use Python natively or use Anaconda (see Chapter 1).
	\item You need to be able to install third-party packages (see Chapter 1). Test this by checking whether you can install the package \texttt{shifterator} and then load it with \texttt{import shifterator} without getting an error.
	\item You need to make sure that your keyboard produces straight quotes \texttt{"} rather than typographical ones when typing. Test that by making sure that you can run \texttt{print("hello world")} in a Jupyter notebook.
	\item Create a folder for this course at an easy to remember place, such as \texttt{/home/damian/bdaca} (Linux), \texttt{/Users/damian/bdaca} (MacOS), or \texttt{c://Users//damian//bdaca} (Windows). You could potentially also use \texttt{c://Users//damian//Desktop//bdaca} (Win) or \texttt{/Users/damian/Desktop/bdaca} (Mac) or similar. Make sure that you can locate files in that folder in Jupyter Notebook. And remember/write down it's name! Preferably, don't use spaces (can lead to confusion), and Windows users, replace \texttt{\textbackslash} by either a double \texttt{\textbackslash \textbackslash} or by forward slashes (/).
\end{itemize}
If -- even after trying -- you do not succeed in any of these steps, ask your classmates. If that also does not help, contact me as soon as possible.


\end{corona}




\chapter{Schedule and Literature}

\input{literature}

\input{schedule}

\bibliographystyle{apacite}
\bibliography{../../resources/literature}



\end{document}


\bibliographystyle{apacite}
\bibliography{../../resources/literature}

 
 
 
\end{document}
