

The course contributes to the following three exit qualifications of the Research Master in Communication Science:


\textit{Expertise in empirical research}


	3.	Knowledge and Understanding: Have in-depth knowledge and a thorough understanding of advanced research designs and methods


	4.	Skills and abilities: Are able, independently and on their own, to set up, conduct, report and interpret advanced academic research.


\textit{Academic abilities and attitudes}


	6.	Attitude: Accept that scientific knowledge is always 'work in progress' and that arguments must be considered and conclusions drawn on the basis of empirical results and valid criticism.


The exit qualifications are elaborated in the following 11 specifications:
3. Knowledge and Understanding: Have in-depth knowledge and a thorough understanding of advanced research designs and methods. 


3.1. Have in-depth knowledge and a thorough understanding of advanced research designs and methods, including their value and limitations.


3.2.	Have in-depth knowledge and a thorough understanding of advanced techniques for data analysis.


4. Skills and abilities: Are able, independently and on their own, to set up, conduct, report and interpret advanced academic research.


4.1	Are able to formulate research questions and hypotheses for advanced empirical studies


4.2	Are able to develop a research plan, choose appropriate and suitable research designs and methods for advanced empirical studies, and justify the underlying choices. 


4.3	Are able to assess the validity and reliability of advanced empirical research, and to judge the scientific and professional value of findings from advanced empirical research.


4.4	Are able to apply advanced empirical research methods.


6. Academic attitudes


6.1 	Regularly asses their own assumptions, strengths and weaknesses critically.


6.2	Accept that scientific knowledge is always 'work in progress' and that something regarded as 'true' may be proven to be false, and vice-versa.


6.3 	Are keen to acquire new knowledge, skills and abilities. 


6.4 	Are willing to share and discuss arguments, results and conclusions, including submitting one's own work to peer review. 


6.5 	Are convinced that academic debates should not be conducted on the basis of rhetorical qualities but that arguments must be considered and conclusions drawn on the basis of empirical results and valid criticism.
