\input{../../resources/preamble}
\addbibresource{../../resources/literature.bib}
\graphicspath{{../../resources/img/}}


\begin{document}

\title[Big Data and Automated Content Analysis]{\textbf{Big Data and Automated Content Analysis (12EC)} 
\\Week 7: »Web Scraping«
\\Wednesday}
\author[Damian Trilling]{Damian Trilling\\ \footnotesize{d.c.trilling@uva.nl, @damian0604 \\}}
\date{March 23, 2022}
\institute[UvA CW]{UvA RM Communication Science}


\begin{frame}{}
	\titlepage
\end{frame}

\begin{frame}{Today}
	\tableofcontents
\end{frame}



\question{Everything clear from last week?}


\begin{frame}{Main points from last week}

\begin{alertblock}{I assume that by now, everybody knows:}
\begin{itemize}
\item how to work with textual data;
\item and in particular (for this week) the concept of regular expressions
\end{itemize}
\end{alertblock}
\end{frame}


\begin{frame}[standout]
This week, we will get a general overview of working with textual data. Combining the knowledge from this week with last week gives you all blocks you need to do cool automated content analyses -- which we will do a lot next block.
\end{frame}


\input{../../modules/scraping/scraping.tex}










\question{Any questions?}

\section{Next steps}

\begin{frame}[standout]
Make sure you understood all of today's concepts.

Re-read the chapters.

On Friday, you will write your own scraper. \textcolor{orange}{Prepare} by choosing a website that you want to scrape. It is advisable to select a site without things like cookiewalls or logins.
\large{\url{https://github.com/uvacw/teaching-bdaca/blob/main/12ec-course/week07/exercises/}}
\end{frame}





\begin{frame}[allowframebreaks,plain]
	\printbibliography
\end{frame}



\end{document}
