\section{Beyond standard data files}
\subsection{API's}

\begin{frame}{Beyond files}
It probably has occured to you by now that


\textcolor{red}{\large{\textbf{it's all about the structure}}}:
\begin{itemize}
	\item<2-> we can write \textit{anything} to files
	\item<3-> it doesn't really matter whether sth is called "csv" or whatever -- as long as we know how records are delimited and what the encoding is
	\item<4-> and $\ldots$ do we then even need files?
\end{itemize}

\end{frame}

\begin{frame}{APIs}
	{\huge{No.}}
	Why not just send a JSON object (with a question/request) directly through the internet and get another one (with an answer/response) back?
	
	That's what (most) Application Programming Interfaces (APIs) do.
	
	\begin{block}{Great if we have a nested data structure}
		\begin{itemize}
			\item<2-> Items within news feeds
			\item<3-> Personal data within authors within books
			\item<4-> Bio statements within authors within tweets
		\end{itemize}
	\end{block}
\end{frame}


\begin{frame}[fragile]{A JSON object containing GoogleBooks data}
	\begin{lstlistingoutput}
{'totalItems': 574, 'items': [{'kind': 'books#volume', 'volumeInfo': {'publisher': '"O\'Reilly Media, Inc."', 'description': u'Get a comprehensive, in-depth introduction to the core Python language with this hands-on book. Based on author Mark Lutz\u2019s popular training course, this updated fifth edition will help you quickly write efficient, high-quality code with Python. It\u2019s an ideal way to begin, whether you\u2019re new to programming or a professional developer versed in other languages. Complete with quizzes, exercises, and helpful illustrations, this easy-to-follow, self-paced tutorial gets you started with both Python 2.7 and 3.3\u2014 the
...
...
'kind': 'books#volumes'}
	\end{lstlistingoutput}
\end{frame}



\begin{frame}{Who offers APIs?}
	The usual suspects: Twitter, Facebook, Google -- but also Reddit, Youtube, \ldots \\~
	\begin{block}{If you ever leave your bag on a bus on Chicago}<2->
		\onslide<3->{
			\ldots but do have Python on your laptop, watch this: \url{https://www.youtube.com/watch?v=RrPZza_vZ3w}. \\
			That guy queries the Chicago bus company's API to calculate when \emph{exactly the vehicle} with his bag arrives the next time at the bus stop in front of his office.
			\\~\\ \tiny{(Yes, he tried calling the help desk before, but they didn't know. He got his bag back.)}
		}
	\end{block}
\end{frame}

\begin{frame}{APIs}
	\begin{block}{Pro}<1->
		\begin{itemize}
			\item Structured data (JSON!)
			\item Easy to process automatically
			\item Can be directy embedded in your script
		\end{itemize}
	\end{block}
	\begin{block}{Con}<2->
		\begin{itemize}
			\item Often limitations (requests per minute, sampling, \ldots)
			\item You have to trust the provider that he delivers the right content
			\item Some APIs won't allow you to go back in time
			\item Some APIs will charge you money for some or all funcitons
		\end{itemize}
	\end{block}



\end{frame}
