\input{../../resources/preamble}
\addbibresource{../../resources/literature.bib}
\graphicspath{{../../resources/img/}}


\begin{document}

\title[Big Data and Automated Content Analysis]{\textbf{Big Data and Automated Content Analysis (12EC)} 
\\Week 5: »Statistical Modelling and Machine learning«
\\Wednesday}
\author[Damian Trilling]{Damian Trilling\\ \footnotesize{d.c.trilling@uva.nl, @damian0604 \\}}
\date{March 9, 2022}
\institute[UvA CW]{UvA RM Communication Science}


\begin{frame}{}
	\titlepage
\end{frame}

\begin{frame}{Today}
	\tableofcontents
\end{frame}



\question{Everything clear from last week?}


\begin{frame}{Main points from last week}

\begin{alertblock}{I assume that by now, everybody knows:}
\begin{itemize}
\item how to get any data, in any shape, in all common file formats, into a structure usable for future analysis;
\item how to create a report in Jupyter Notebook using Markdown cells as well as matplotlib and seaborn (optionally: other visualization libraries).
\end{itemize}
\end{alertblock}
\end{frame}


\begin{frame}[standout]
This week, we will get a general overview of ML and statistical modelling. In Part II of the course, we will go more in-depth and specifically use these techniques in combination with textual data.
\end{frame}


\input{../../modules/machinelearning-intro/overview.tex}

\input{../../modules/machinelearning-intro/supervised.tex}

\input{../../modules/machinelearning-intro/unsupervised.tex}







\question{Any questions?}

\section{Next steps}

\begin{frame}[standout]
Take-home exam on Friday!
\end{frame}


\begin{frame}[standout]
Make sure you understood all of today's concepts.

Re-read the chapters.

I prepared exercises to work on \emph{during} the Friday meeting (alone or in teams):
\large{\url{https://github.com/uvacw/teaching-bdaca/blob/main/12ec-course/week05/exercises/}}
\end{frame}





\begin{frame}[allowframebreaks,plain]
	\printbibliography
\end{frame}



\end{document}
